Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-11-09 tex/scam/paper-submit.tex
initial commit

\documentclass[12pt,pdftex,aos,noinfoline]{imsart}
%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}

@@

\renewcommand{\baselinestretch}{1.1}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}

@@

\begin{aug}
\vskip10pt
\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
\comma 
\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
\and
\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
\address{
\begin{tabular}{ccc}
\\[10pt]
Machine Learning Department & Department of Statistics & Department of Statistics\\
Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
& & University of Chicago
\end{tabular}
%\\[20pt]
%\printead{e1,e2,e3}
}
\end{aug}

@@

\input{introduction}
\input{summary}
\input{additive_faithful}
\input{estimation}
\input{optimization}
\input{sparsistency}
\input{experiments}
\input{discussion}
\input{appendix}

%\newpage
%\input{notes}

@@

>>>>

\documentclass[12pt,pdftex,aos,noinfoline,addressasfootnote]{imsart}
%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}

@@

\renewcommand{\baselinestretch}{1.05}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}

@@

\begin{aug}
\vskip10pt
\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
\comma 
\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
\and
\author{\fnms{John}
  \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
\address{Machine Learning Department, Carnegie Mellon University,
  Pittsburgh PA 15213}
\address{Department of Statistics, University of Chicago, Chicago IL 60637}
\end{aug}

@@

\input{introduction}
\input{summary}
\input{additive_faithful}
\input{estimation}
\input{optimization}
\input{sparsistency}
\input{experiments}
\input{discussion}
%\newpage
%\input{notes}

@@

\clearpage
\input{supplement}
